\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{url}

\input{mathhelper}
\input{theorems}
\input{unicode}
\input{skin}
\input{tikztemplate}

\title{Preambles}
\author{Tianyi Pu}
\date{\today}

\begin{document}

\maketitle

\section{Math Commands}
\begin{itemize}
    \item[\texttt{\textbackslash abs[1]}] $\abs{\#1}$, the absolute value.
    \item[\texttt{\textbackslash arcosh}] $\arcosh$, the inverse hyperbolic cosine.
    \item[\texttt{\textbackslash arcoth}] $\arcoth$, the inverse hyperbolic cotangent.
    \item[\texttt{\textbackslash arcsch}] $\arcsch$, the inverse hyperbolic cosecant.
    \item[\texttt{\textbackslash arsech}] $\arsech$, the inverse hyperbolic secant.
    \item[\texttt{\textbackslash arsinh}] $\arsinh$, the inverse hyperbolic sine.
    \item[\texttt{\textbackslash artanh}] $\artanh$, the inverse hyperbolic tangent.
    \item[\texttt{\textbackslash Atop[2]}] $\Atop{\#1}{\#2}$, a safe wrapping of \texttt{\textbackslash atop}, the line-less fraction.
    \item[\texttt{\textbackslash Beta}] $\Beta$, the big $\beta$.
    \item[\texttt{\textbackslash ceil[1]}] $\ceil{\#1}$, rounding up.
    \item[\texttt{\textbackslash csch}] $\csch$, the hyperbolic cosecant.
    \item[\texttt{\textbackslash d}] $\d$, the differential operator.
    \item[\texttt{\textbackslash diag}] $\diag$, a diagonal matrix.
    \item[\texttt{\textbackslash erfc}] $\erfc$, the complementary error function.
    \item[\texttt{\textbackslash f[1]}] $\f{\#1}$, a lazy wrapping of \texttt{\textbackslash left(\#1\textbackslash right)}.
    \item[\texttt{\textbackslash floor[1]}] $\floor{\#1}$, rounding down.
    \item[\texttt{\textbackslash half[1][1]}] $\half[\#1]$, a lazy wrapping of halves.
    \item[\texttt{\textbackslash hypergeometric[5]}] $\hypergeometric{\#1}{\#2}{\#3}{\#4}{\#5}$, the hypergeometric function with arguments.
    \item[\texttt{\textbackslash hypergeometricOlver[5]}] $\hypergeometricOlver{\#1}{\#2}{\#3}{\#4}{\#5}$, the Olver's hypergeometric function with arguments.
    \item[\texttt{\textbackslash identity}] $\identity$, the identity operator.
    \item[\texttt{\textbackslash innerproduct[1]}] $\innerproduct{\#1}$, the inner product.
    \item[\texttt{\textbackslash Li}] $\Li$, the polylogarithm function.
    \item[\texttt{\textbackslash pFq[2]}] $\pFq{\#1}{\#2}$, the hypergeometric function.
    \item[\texttt{\textbackslash pFqOlver[2]}] $\pFqOlver{\#1}{\#2}$, the hypergeometric function.
    \item[\texttt{\textbackslash sech}] $\sech$, the hyperbolic secant.
    \item[\texttt{\textbackslash sign}] $\sign$, the sign function.
    \item[\texttt{\textbackslash spanspace}] $\spanspace$, the span space.
    \item[\texttt{\textbackslash supp}] $\supp$, the function support.
    \item[\texttt{\textbackslash tceil[1]}] $\tceil{\#1}$, rounding up with tiny delimiter.
    \item[\texttt{\textbackslash tfloor[1]}] $\tfloor{\#1}$, rounding down with tiny delimiter.
\end{itemize}

\section{Theorem environments}
\begin{theorem}
    This is a theorem.
\end{theorem}
\begin{corollary}
    This is a corollary.
\end{corollary}
\begin{proposition}
    This is a proposition.
\end{proposition}
\begin{lemma}
    This is a lemma.
\end{lemma}
\begin{conjecture}
    This is a conjecture.
\end{conjecture}

\begin{remark}
    This is a remark.
\end{remark}

\begin{example}
    This is an example.
\end{example}

\section{Unicode characters}
⬯✗□×

\nocite{*}
\bibliographystyle{plain}
\bibliography{references}

\end{document}
